Shades of Green

### 2023-09-26 docs/presentations/20230928-sehm_presentation.qmd
fix new labels in interactive eco-innovation plot

## Research Questions

1.
2.
3.

@@

```{python}
plot_eco_innovation_by_bioeconomy_vision_interactive(
    eco_innovation_by_bioeconomy_visions
).show()

>>>>

## Research Questions {.fragment}

1. How innovative is the Swedish forest bioeconomy?
2. What visions of a bioeconomy are represented?
3. What eco-innovations are developed?

@@

```{python}
plot_eco_innovation_by_bioeconomy_vision_interactive(
    eco_innovation_by_bioeconomy_visions, codes_df
).show()
